cola Report for Hierarchical Partitioning - 'GrunPancreas'
==================

**Date**: `r format(as.POSIXlt(Sys.time()), usetz = TRUE)`, **cola version**: `r installed.packages()["cola", "Version"]`

----------------------------------------------------------------

<style type='text/css'>

body, td, th {
   font-family: Arial,Helvetica,sans-serif;
   background-color: white;
   font-size: 13px;
  max-width: 800px;
  margin: auto;
  margin-left:210px;
  padding: 0px 10px 0px 10px;
  border-left: 1px solid #EEEEEE;
  line-height: 150%;
}

tt, code, pre {
   font-family: 'DejaVu Sans Mono', 'Droid Sans Mono', 'Lucida Console', Consolas, Monaco, 

monospace;
}

h1 {
   font-size:2.2em;
}

h2 {
   font-size:1.8em;
}

h3 {
   font-size:1.4em;
}

h4 {
   font-size:1.0em;
}

h5 {
   font-size:0.9em;
}

h6 {
   font-size:0.8em;
}

a {
  text-decoration: none;
  color: #0366d6;
}

a:hover {
  text-decoration: underline;
}

a:visited {
   color: #0366d6;
}

pre, img {
  max-width: 100%;
}
pre {
  overflow-x: auto;
}
pre code {
   display: block; padding: 0.5em;
}

code {
  font-size: 92%;
  border: 1px solid #ccc;
}

code[class] {
  background-color: #F8F8F8;
}

table, td, th {
  border: 1px solid #ccc;
}

blockquote {
   color:#666666;
   margin:0;
   padding-left: 1em;
   border-left: 0.5em #EEE solid;
}

hr {
   height: 0px;
   border-bottom: none;
   border-top-width: thin;
   border-top-style: dotted;
   border-top-color: #999999;
}

@media print {
   * {
      background: transparent !important;
      color: black !important;
      filter:none !important;
      -ms-filter: none !important;
   }

   body {
      font-size:12pt;
      max-width:100%;
   }

   a, a:visited {
      text-decoration: underline;
   }

   hr {
      visibility: hidden;
      page-break-before: always;
   }

   pre, blockquote {
      padding-right: 1em;
      page-break-inside: avoid;
   }

   tr, img {
      page-break-inside: avoid;
   }

   img {
      max-width: 100% !important;
   }

   @page :left {
      margin: 15mm 20mm 15mm 10mm;
   }

   @page :right {
      margin: 15mm 10mm 15mm 20mm;
   }

   p, h2, h3 {
      orphans: 3; widows: 3;
   }

   h2, h3 {
      page-break-after: avoid;
   }
}
</style>

```{r, echo = FALSE, message = FALSE}
library(knitr)
library(markdown)
options(markdown.HTML.options = setdiff(c(getOption("markdown.HTML.options")), "base64_images"))
options(width = 100)
options(digits = 3)
opts_chunk$set(
    comment = "#>",
    fig.path = "figure_cola/",
    warning = FALSE,
    message = FALSE
)
suppressPackageStartupMessages(library(ComplexHeatmap))
suppressPackageStartupMessages(library(genefilter))
ht_opt$message = FALSE

n_cores = cola:::get_nc(cores)
```


## Summary



First the variable is renamed to `res_rh`.

```{r, eval = FALSE, echo = TRUE}
res_rh = rh
```

```{r, echo = FALSE}
res_rh = object
```

The partition hierarchy and all available functions which can be applied to `res_rh` object.

```{r}
res_rh
```

The call of `hierarchical_partition()` was:

```{r, echo = FALSE}
cat(paste(deparse(res_rh@call, width.cutoff = 80), collapse = "\n"), "\n")
```

Dimension of the input matrix:

```{r}
mat = get_matrix(res_rh)
dim(mat)
```

All the methods that were tried:

```{r}
res_rh@param$combination_method
```

### Density distribution

The density distribution for each sample is visualized as one column in the following heatmap.
The clustering is based on the distance which is the Kolmogorov-Smirnov statistic between two distributions.

```{r, echo = FALSE, message = FALSE}
t1 = Sys.time()
message(qq("* making density heatmap of global distribution for each sample (@{ncol(mat)} samples)"), appendLF = FALSE)
```

```{r density-heatmap}
library(ComplexHeatmap)
densityHeatmap(mat, top_annotation = HeatmapAnnotation(df = get_anno(res_rh), 
    col = get_anno_col(res_rh)), ylab = "value", cluster_columns = TRUE, show_column_names = FALSE,
    mc.cores = 1)
```

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1))))
```

Some values about the hierarchy:

```{r}
all_nodes(res_rh)
all_leaves(res_rh)
node_info(res_rh)
```

In the output from `node_info()`, there are the following columns:

- `id`: The node id.
- `best_method`: The best method selected.
- `depth`: Depth of the node in the hierarchy.
- `best_k`: Best number of groups of the partition on that node.
- `n_columns`: Number of columns in the submatrix.
- `n_signatures`: Number of signatures with the `best_k`.
- `p_signatures`: Proportion of hte signatures in total number of rows in the matrix.
- `is_leaf`: Whether the node is a leaf.

Labels of nodes are encoded in a special way. The number of digits
correspond to the depth of the node in the hierarchy and the value of the
digits correspond to the index of the subgroup in the current node, E.g. a label
of “012” means the node is the second subgroup of the partition which is the
first subgroup of the root node.

### Suggest the best k

```{r, echo = FALSE, message = FALSE}
message("* suggesting the best k for each node")
```

Following table shows the best `k` (number of partitions) for each node in the
partition hierarchy. Clicking on the node name in the table goes to the
corresponding section for the partitioning on that node.

[The cola vignette](https://jokergoo.github.io/cola_vignettes/cola.html#toc_13)
explains the definition of the metrics used for determining the best
number of partitions.


```{r, eval = FALSE}
suggest_best_k(res_rh)
```

```{r, echo = FALSE}
tb = suggest_best_k(res_rh)
stop_reason = attr(tb, "stop_reason")
stop_reason = sapply(stop_reason, function(x) {
    if(is.null(x)) {
        return(NA)
    } else {
        return(cola:::STOP_REASON_INDEX[x])
    }
})

tb = cbind(node_id = paste0("Node", rownames(tb)), tb, stringsAsFactors = FALSE)

tb$node_id[!tb$is_leaf] = qq("[Node@{tb$node[!tb$is_leaf]}](#Node@{tb$node[!tb$is_leaf]})", collapse = FALSE)
tb$node_id[tb$is_leaf] = qq("Node@{tb$node[tb$is_leaf]}-leaf", collapse = FALSE)
tb$is_leaf = ifelse(tb$is_leaf, "\u2713", "")

tb$is_leaf = ifelse(is.na(stop_reason), tb$is_leaf, paste0(tb$is_leaf, " (", stop_reason, ")"))
tb$is_leaf = gsub("c", "&#99;", tb$is_leaf)
colnames(tb) = c("Node", "Code", "Best method", "Is leaf", "Best k", "1-PAC", "Mean silhouette", "Concordance", "#samples", "")
tb[, "1-PAC"] = sprintf("%.2f", tb[, "1-PAC"])
tb[, "Mean silhouette"] = sprintf("%.2f", tb[, "Mean silhouette"])
tb[, "Concordance"] = sprintf("%.2f", tb[, "Concordance"])
tb[is.na(tb[, "Best k"]), "Best k"] = ""
tb[tb[, "1-PAC"] == "NA", "1-PAC"] = ""
tb[tb[, "Mean silhouette"] == "NA", "Mean silhouette"] = ""
tb[tb[, "Concordance"] == "NA", "Concordance"] = ""
tb[tb[, 3] == "not applied", 3] = "<span style='color:grey;'><i>not applied</i></span>"
kable(tb[, -2], row.names = FALSE)
```


```{r, echo = FALSE, results = "asis"}
reasons = sort(unique(stop_reason[!is.na(stop_reason)]))
if(length(reasons) > 0) cat("Stop reason: ")
for(i in seq_along(reasons)) {
    cat(reasons[i], ") ", names(which(cola:::STOP_REASON_INDEX == reasons[i])), " ", sep = "")
}
cat("\n\n\\*\\*: 1-PAC > 0.95, \\*: 1-PAC > 0.9")
```


### Partition hierarchy

The nodes of the hierarchy can be merged by setting the `merge_node` parameters. Here we 
control the hierarchy with the `min_n_signatures` parameter. The value of `min_n_signatures` is
from `node_info()`.


```{r, echo = FALSE, message = FALSE}
t1 = Sys.time()
message(qq("* collecting classifications for each ndoe height"), appendLF = FALSE)
```

```{r, results = "asis", echo = FALSE, include = TRUE}
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 362))', 'n_signatures \u2265 362', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 519))', 'n_signatures \u2265 519', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 644))', 'n_signatures \u2265 644', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 671))', 'n_signatures \u2265 671', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 715))', 'n_signatures \u2265 715', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 858))', 'n_signatures \u2265 858', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 973))', 'n_signatures \u2265 973', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 994))', 'n_signatures \u2265 994', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 1106))', 'n_signatures \u2265 1106', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 1406))', 'n_signatures \u2265 1406', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 1887))', 'n_signatures \u2265 1887', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 1958))', 'n_signatures \u2265 1958', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 2465))', 'n_signatures \u2265 2465', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 2575))', 'n_signatures \u2265 2575', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 6804))', 'n_signatures \u2265 6804', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 6863))', 'n_signatures \u2265 6863', prefix = 'collect-classes-from-hierarchical-partition')
knitr_add_tab_item('collect_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 7174))', 'n_signatures \u2265 7174', prefix = 'collect-classes-from-hierarchical-partition')
knitr_insert_tabs('collect-classes-from-hierarchical-partition')
```

Following shows the table of the partitions (You need to click the **show/hide
code output** link to see it).

```{r, results = "asis", echo = FALSE, include = TRUE}
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 362))', 'n_signatures \u2265 362', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 519))', 'n_signatures \u2265 519', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 644))', 'n_signatures \u2265 644', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 671))', 'n_signatures \u2265 671', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 715))', 'n_signatures \u2265 715', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 858))', 'n_signatures \u2265 858', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 973))', 'n_signatures \u2265 973', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 994))', 'n_signatures \u2265 994', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 1106))', 'n_signatures \u2265 1106', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 1406))', 'n_signatures \u2265 1406', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 1887))', 'n_signatures \u2265 1887', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 1958))', 'n_signatures \u2265 1958', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 2465))', 'n_signatures \u2265 2465', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 2575))', 'n_signatures \u2265 2575', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 6804))', 'n_signatures \u2265 6804', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 6863))', 'n_signatures \u2265 6863', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_add_tab_item('get_classes(res_rh, merge_node = merge_node_param(min_n_signatures = 7174))', 'n_signatures \u2265 7174', prefix = 'get-classes-from-hierarchical-partition', hide_and_show = TRUE)
knitr_insert_tabs('get-classes-from-hierarchical-partition')
```



### Top rows heatmap

Heatmaps of the top rows:


```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* making top row heatmaps"), appendLF = FALSE)
```

```{r top-rows-heatmap, fig.width = 3.5, fig.height = 3.5}
top_rows_heatmap(res_rh)
```

Top rows on each node:

```{r top-rows-overlap, fig.width = 8, fig.height = 6}
top_rows_overlap(res_rh, method = "upset")
```


### UMAP plot

UMAP plot which shows how samples are separated.

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* making dimension reduction plots"), appendLF = FALSE)
```

```{r, results = 'asis', echo = FALSE, include = TRUE}
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 362),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 362),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 362', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 519),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 519),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 519', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 644),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 644),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 644', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 671),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 671),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 671', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 715),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 715),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 715', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 858),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 858),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 858', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 973),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 973),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 973', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 994),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 994),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 994', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 1106),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 1106),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 1106', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 1406),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 1406),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 1406', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 1887),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 1887),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 1887', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 1958),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 1958),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 1958', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 2465),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 2465),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 2465', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 2575),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 2575),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 2575', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 6804),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 6804),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 6804', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 6863),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 6863),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 6863', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_add_tab_item('par(mfrow = c(1, 2))
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 7174),
    method = "UMAP", top_value_method = "SD", top_n = 1000, scale_rows = FALSE)
dimension_reduction(res_rh, merge_node = merge_node_param(min_n_signatures = 7174),
    method = "UMAP", top_value_method = "ATC", top_n = 1000, scale_rows = TRUE)', 'n_signatures \u2265 7174', prefix = 'dimension-reduction-by-depth', opt = "fig.width = 14, fig.height = 7, out.width = '100%'")
knitr_insert_tabs('dimension-reduction-by-depth')
```




### Signature heatmap

Signatures on the heatmap are the union of all signatures found on every node
on the hierarchy. The number of k-means on rows are automatically selected by the function.

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* making signature heatmaps"), appendLF = FALSE)
```

```{r, results = 'asis', echo = FALSE, include = TRUE}
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 362))', 'n_signatures \u2265 362', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 519))', 'n_signatures \u2265 519', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 644))', 'n_signatures \u2265 644', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 671))', 'n_signatures \u2265 671', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 715))', 'n_signatures \u2265 715', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 858))', 'n_signatures \u2265 858', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 973))', 'n_signatures \u2265 973', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 994))', 'n_signatures \u2265 994', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 1106))', 'n_signatures \u2265 1106', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 1406))', 'n_signatures \u2265 1406', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 1887))', 'n_signatures \u2265 1887', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 1958))', 'n_signatures \u2265 1958', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 2465))', 'n_signatures \u2265 2465', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 2575))', 'n_signatures \u2265 2575', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 6804))', 'n_signatures \u2265 6804', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 6863))', 'n_signatures \u2265 6863', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_add_tab_item('get_signatures(res_rh, merge_node = merge_node_param(min_n_signatures = 7174))', 'n_signatures \u2265 7174', opt = 'results="hide"', prefix = 'get-signatures-from-hierarchical-partition')
knitr_insert_tabs('get-signatures-from-hierarchical-partition')
```

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1))));
```


Compare signatures from different nodes:

```{r, prefix = "comapre_signatures-from-hierarchical-partition"}
compare_signatures(res_rh, verbose = FALSE)
```

If there are too many signatures, `top_signatures = ...` can be set to only show the 
signatures with the highest FDRs. Note it only works on every node and the final signatures
are the union of all signatures of all nodes.

```{r, eval = FALSE}
# code only for demonstration
# e.g. to show the top 500 most significant rows on each node.
tb = get_signature(res_rh, top_signatures = 500)
```


### Test to known annotations

Test correlation between subgroups and known annotations. If the known
annotation is numeric, one-way ANOVA test is applied, and if the known
annotation is discrete, chi-squared contingency table test is applied.

```{r, echo = FALSE, message = FALSE}
message(qq("* testing correlation of subgroups to known annotations"))
```

```{r, results = 'asis', echo = FALSE, include = TRUE}
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 362))', 'n_signatures \u2265 362', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 519))', 'n_signatures \u2265 519', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 644))', 'n_signatures \u2265 644', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 671))', 'n_signatures \u2265 671', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 715))', 'n_signatures \u2265 715', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 858))', 'n_signatures \u2265 858', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 973))', 'n_signatures \u2265 973', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 994))', 'n_signatures \u2265 994', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 1106))', 'n_signatures \u2265 1106', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 1406))', 'n_signatures \u2265 1406', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 1887))', 'n_signatures \u2265 1887', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 1958))', 'n_signatures \u2265 1958', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 2465))', 'n_signatures \u2265 2465', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 2575))', 'n_signatures \u2265 2575', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 6804))', 'n_signatures \u2265 6804', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 6863))', 'n_signatures \u2265 6863', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_add_tab_item('test_to_known_factors(res_rh, merge_node = merge_node_param(min_n_signatures = 7174))', 'n_signatures \u2265 7174', prefix = 'test-to-known-factors-from-hierarchical-partition')
knitr_insert_tabs('test-to-known-factors-from-hierarchical-partition')
```



## Results for each node

```{r, results = "asis", echo = FALSE}
fs = 2
is_hc = TRUE
single_report = FALSE
all_parents = setdiff(all_nodes(res_rh), all_leaves(res_rh))
# all_parents = all_nodes(res_rh)
n_section = length(all_parents)
i_section = 0
.e = environment()
all_k = res_rh@list[[1]]@k
registerDoParallel(cores)

md_list <- foreach (ind = seq_along(all_parents)) %dopar% {
    i_section = ind
    node = all_parents[ind]
    top_value_method = res_rh[[node]]@top_value_method
    partition_method = res_rh[[node]]@partition_method
    
    tmpfile = tempfile(tmpdir = cola:::.ENV$TEMP_DIR)
    
    brew(file.path(cola:::TEMPLATE_DIR, "section_template.Rmd-template"), tmpfile)
    rmd = paste(readLines(tmpfile), collapse = "\n")
    file.remove(tmpfile)

    ComplexHeatmap:::dev.null()
    txt = knit(text = rmd, quiet = TRUE, envir = .e)
    devlt = dev.list()
    if(names(devlt)[1] == "quartz_off_screen") {
        invisible(dev.off())
    }
    dev.off()
    return(txt)
}
stopImplicitCluster()

for(i in seq_along(md_list)) {
    cat(md_list[[i]], "\n")
}
```

## Session info

```{r}
sessionInfo()
```


```{r, echo = FALSE, message = FALSE}
message("-----------------------------------------------------------------")
```

